---
title: "CCF Plots"
date: "06/23/2014"
output: pdf_document
classoption: landscape
fig_width: 8
fig_height: 8
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

These are CCF plots of the pairwise country comparisons for the Ofenbach track HSKT. Notice which countries are lagging, and if the lag occur at the same h.

## Cross Covariance Function plots

How to interpret: Austria for instance, lags France. The streams of the predicted country (Austria) lag positively behind France. The most dominant cross covariances in this case occur around h=-12. 

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width=2.2, fig.height=3}

library(tidyverse)
charts <- read_tsv('/cloud/project/raw/weekly_offennbach.tsv')
charts_total <- charts %>%
  filter(COUNTRY_CODE %in% c("FR", "LU", "LT", "DE", "PL", "BE",
                             "CH",  "AT", "WW", "RO", "NO", "HU", "SE", "FI")) %>%
  filter(PRODUCT_TITLE == "Head Shoulders Knees & Toes (feat. Norma Jean Martine)") %>%
  select(COUNTRY_CODE, TOTAL_STREAMS, DATE_KEY)
## Step 1A: reshape
test <- charts_total %>%
  select(TOTAL_STREAMS, COUNTRY_CODE, DATE_KEY) %>%
  group_by_at(vars(-TOTAL_STREAMS)) %>%
  dplyr::mutate(row_id = 1:n()) %>%
  ungroup() %>%
  spread(key = COUNTRY_CODE, value = TOTAL_STREAMS)
test[is.na(test)] = 0
## scale each column
test$AT <- scale(test$AT)
test$BE <- scale(test$BE)
test$CH <- scale(test$CH)
test$DE <- scale(test$DE)
test$FI <- scale(test$FI)
test$FR <- scale(test$FR)
test$HU <- scale(test$HU)
test$LT <- scale(test$LT)
test$LU <- scale(test$LU)
test$NO <- scale(test$NO)
test$PL <- scale(test$PL)
test$RO <- scale(test$RO)
test$SE <- scale(test$SE)
### France by other countries


outcome_vector <- c(3:15)
vector<-c(1:12)

for (b in 1:length(outcome_vector)){
  print(paste0("Plots for the predicted country of", colnames(test[outcome_vector[b]])))
for (i in 1:length(vector)){
DV = ts(test[outcome_vector[b]])
IV = ts(test[vector[i]+3])
ccfvalues = ccf(as.numeric(IV), as.numeric(DV), main = paste0(colnames(test[,vector[i]+3]), "vs", colnames(test[outcome_vector[b]])),
                type = "correlation")
}
}



```


